---
title: "Benford Assignment"
author: "Dave Anderson"
date: "November 28, 2018"
output: pdf_document
---
```{r, echo=FALSE, message=FALSE}
library(benford.analysis)
library(tidyverse)
```


To investigate the effect of increasing sample size on relation to Benford's Law, I chose to use Fibonacci numbers. I started with the first 100 numbers of the sequence and performed Benford's analysis on the first two leading digits.

#100 Numbers
```{r, echo=FALSE}
####100 Fibonacci Numbers
num <- 100
fib <- numeric(num)
fib[1] <- 1
fib[2] <- 1
for (i in 3:num) { 
  fib[i] <- fib[i-1]+fib[i-2]
} 

bfd1 <- benford(fib,number.of.digits = 2)
plot(bfd1)
head(suspectsTable(bfd1),10)
```
There is clearly a staggered pattern in the numbers, which creates a very interesting pattern on the chi-squared difference plot. 

#500 Numbers
```{r,echo=FALSE}
num2 <- 500
fib2 <- numeric(num2)
fib2[1] <- 1
fib2[2] <- 1
for(i in 3:num2) {
  fib2[i] <- fib2[i-1]+fib2[i-2]
}

bfd2 <- benford(fib2)
plot(bfd2)
```

Increasing our numbers from 100 to 500 has made a big difference in our analysis. The distribution of digits seems to conform to Benford very well. The pattern in the chi-squared difference is still evident, but the differences have decreased dramtically. 

#10,000 numbers
```{r,echo=FALSE}
###10,000 Fibonacci Numbers
num3 <- 10000
fib3 <- numeric(num3)
fib3[1] <- 1
fib3[2] <- 1
for (i in 3:num3) {
  fib3[i] <- fib3[i-1]+fib2[i-2]
}
bfd3 <- benford(fib3)
plot(bfd3)

head(suspectsTable(bfd3),10)

bfd4 <- benford(fib3, number.of.digits = 2)
```

Interestingly, it seems as if increasing numbers to 10,000 is actually further from Benford's distribution in some ways. Overall, the pattern from the chi-squared difference has decreased, and most digits are closer to the law, but some digits, such as 20, have strayed further away. It is interesting that many multiples of tens are seen in the suspects list. 
