---
title: "Benford"
author: "Tingrui Huang"
date: "November 26, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r }
library(benford.analysis)
library(BenfordTests)
library(tidyverse)
```

### Census 2000
```{r }
data("census.2000_2010")
census2000_bfd <- benford(census.2000_2010$pop.2000)
plot(census2000_bfd)
MAD(census2000_bfd)
chisq(census2000_bfd)
# Get suspecious value from the data
suspects_2000 <- getSuspects(bfd = census2000_bfd, data = census.2000_2010)
```
For the Year of 2000 census data, generally we have a pretty good result from the benford analysis. However, we have a few abnormal test results for the sequence starts with 2 and 3. From the Chi-squared test, we have a p-value of 0.5207 and it would indicate fail to reject the null hypothesis, which indicates that the distribution of the data is very close to the distribution of Benford Law.

### Census 2010
```{r }
census2010_bfd <- benford(census.2000_2010$pop.2010)
plot(census2010_bfd)
MAD(census2010_bfd)
chisq(census2010_bfd)
# Get suspecious value from the data
suspects_2010 <- getSuspects(bfd = census2010_bfd, data = census.2000_2010)
```
For the Year of 2010 census data, generally we have a pretty good result from the benford analysis. However, we have a few abnormal test results for the sequence starts with 2, 3 and 7. From the Chi-squared test, we have a p-value of 0.6646 and it would indicate fail to reject the null hypothesis, which indcates that the distribution of the data is very close to the distribution of Benford Law.


