---
title: "Group assignment"
author: "Dave Anderson, Longhao Chen, Tingrui Huang, Yudi Mao"
date: "11/26/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(benford.analysis) # loads package data(corporate.payment) # loads data
#This step is to find datasets provided in the package.
d <- data(package = "benford.analysis")
## names of data sets in the package
#d$results[, "Item"]
data(census.2009)

census1 <- benford(census.2009$pop.2009, number.of.digits = 1, sign = "positive", discrete = TRUE, round = 3)
census2 <- benford(census.2009$pop.2009, number.of.digits = 2, sign = "positive", discrete = TRUE, round = 3)
plot(census1)
plot(census2)
```
By looking at the general information of the dataset. We can see that the values of mean, variance, Ex.Kurtosis and skewness well match with the expected values of 0.5
```{r}
census
```


```{r}
#This step is to find the suspicious targets.
suspects <- getSuspects(census, census.2009)
suspects
```

From the suspect function, we can see that Alabama state has a handful of data that are suspicious.





## Chinese city population data

#data source: http://www.citypopulation.de/China-UA.html

```{r}

library(tidyverse)
library(benford.analysis) # loads package data(corporate.payment) # loads data
library(readxl)
chinese_cencus <- read_excel("chinese cencus.xlsx")
df <- na.omit(chinese_cencus)
df1 <- select(df, Population, Population__1, Population__2)



bfd.pop <- benford(as.numeric(df1$Population),
                  number.of.digits = 1)
plot(bfd.pop) #Census 1990
bfd.pop1 <- benford(as.numeric(df1$Population__1),
                   number.of.digits = 1)
plot(bfd.pop1) #Census 2000
bfd.pop2 <- benford(as.numeric(df1$Population__2),
                    number.of.digits = 1)
plot(bfd.pop2) #Census 2010
```

The results do not well fit benford law. The reason could be:
1. Dataset is relatively small (132 obs only)
2. Data is not complete. This dataset only contains population of those cities over 750,000, and they are urban populations.