---
title: "Group assignment"
author: "Dave Anderson, Longhao Chen, Tingrui Huang, Yudi Mao"
date: "11/26/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(benford.analysis) # loads package data(corporate.payment) # loads data
#This step is to find datasets provided in the package.
d <- data(package = "benford.analysis")
## names of data sets in the package
#d$results[, "Item"]
data(census.2009)

#The first code is to look at the high level test of reasonableness.
census1 <- benford(census.2009$pop.2009, number.of.digits = 1, sign = "positive", discrete = TRUE, round = 3)
#We can take a closer look at the first two digits, which is designed to select audit targets.
census2 <- benford(census.2009$pop.2009, number.of.digits = 2, sign = "positive", discrete = TRUE, round = 3)

plot(census1)
#From this plot we can see that rea dotted line, which is the benford line, generally matches good with the bar plot. There are some disgrepencies for the second order test starting at 3 digits.

plot(census2)
#This plot reveals a closer look at first two digits data.

```
By looking at the general information of the dataset. We can see that the values of mean, variance, Ex.Kurtosis and skewness well match with the expected values of 0.5, 0.0833, -1.2, and 0.
```{r}
census1
```


```{r}
#This step is to find the suspicious targets using the first 2 digits Benford model.
suspects <- getSuspects(census2, census.2009)
suspects
```

From the suspect function, we can see that Alabama state has a handful of data that are suspicious.

### Census 2000
```{r }
data("census.2000_2010")
census2000_bfd <- benford(census.2000_2010$pop.2000)
plot(census2000_bfd)
MAD(census2000_bfd)
chisq(census2000_bfd)
# Get suspecious value from the data
suspects_2000 <- getSuspects(bfd = census2000_bfd, data = census.2000_2010)
```
For the Year of 2000 census data, generally we have a pretty good result from the benford analysis. However, we have a few abnormal test results for the sequence starts with 2 and 3. From the Chi-squared test, we have a p-value of 0.5207 and it would indicate fail to reject the null hypothesis, which indicates that the distribution of the data is very close to the distribution of Benford Law.

### Census 2010
```{r }
census2010_bfd <- benford(census.2000_2010$pop.2010)
plot(census2010_bfd)
MAD(census2010_bfd)
chisq(census2010_bfd)
# Get suspecious value from the data
suspects_2010 <- getSuspects(bfd = census2010_bfd, data = census.2000_2010)
```
For the Year of 2010 census data, generally we have a pretty good result from the benford analysis. However, we have a few abnormal test results for the sequence starts with 2, 3 and 7. From the Chi-squared test, we have a p-value of 0.6646 and it would indicate fail to reject the null hypothesis, which indcates that the distribution of the data is very close to the distribution of Benford Law.

## Chinese city population data

#data source: http://www.citypopulation.de/China-UA.html

```{r}

library(tidyverse)
library(benford.analysis) # loads package data(corporate.payment) # loads data
library(readxl)
chinese_cencus <- read_excel("chinese cencus.xlsx")
df <- na.omit(chinese_cencus)
df1 <- select(df, Population, Population__1, Population__2)



bfd.pop <- benford(as.numeric(df1$Population),
                  number.of.digits = 1)
plot(bfd.pop) #Census 1990
bfd.pop1 <- benford(as.numeric(df1$Population__1),
                   number.of.digits = 1)
plot(bfd.pop1) #Census 2000
bfd.pop2 <- benford(as.numeric(df1$Population__2),
                    number.of.digits = 1)
plot(bfd.pop2) #Census 2010
```

The results do not well fit benford law. The reason could be:
1. Dataset is relatively small (132 obs only)
2. Data is not complete. This dataset only contains population of those cities over 750,000, and they are urban populations.